---
title: Basic Deterministic Trees
output: github_document
---

```{r, message = F, warning = F}
library(tidyverse)
```

Early attempts at making, storing, and drawing line segments.
```{r}
gr <- 1.272018

X0 <- rep(0, 100)
Y0 <- seq(0, 1, length.out = 100)

theta_0 <- 0
b_0 <- tibble(x = round(X0*cos(theta_0) - Y0*sin(theta_0), 3),
              y = round(X0*sin(theta_0) + Y0*cos(theta_0), 3),
              branch = rep("0",100),
              thickness = seq(1, 1/gr, length.out = 100))
tree <- b_0

ggplot(tree) + 
  geom_point(aes(x, y, size = thickness)) +
  coord_fixed() + theme(legend.position="none")
```

Try to rotate
```{r}
X1 <- rep(0, 100)
Y1 <- seq(0, 1/gr, length.out = 100)

theta_01a = theta_0 + pi/6
b_01a <- tibble(x = round(X1*cos(theta_01a) - Y1*sin(theta_01a) + b_0$x[100], 3),
                y = round(X1*sin(theta_01a) + Y1*cos(theta_01a) + b_0$y[100], 3),
                branch = rep("1a", 100),
                thickness = seq(1/gr,1/gr^2, length.out = 100))

tree <- rbind(tree,b_01a)

theta_01b = theta_0 - pi/6
b_01b <- tibble(x = round(X1*cos(theta_01b) - Y1*sin(theta_01b) + b_0$x[100], 3),
                y = round(X1*sin(theta_01b) + Y1*cos(theta_01b) + b_0$y[100], 3),
                branch = rep("1b", 100),
                thickness = seq(1/gr,1/gr^2, length.out = 100))

tree <- rbind(tree,b_01b)

ggplot(tree) + 
  geom_point(aes(x, y, size = thickness)) + 
  coord_fixed() + theme(legend.position="none")
```

Adding branches to branches
```{r}
X2 <- rep(0, 100)
Y2 <- seq(0, 1/gr^2, length.out = 100)

theta_01a2a = theta_01a + pi/6/gr
b_01a2a <- tibble(x = round(X2*cos(theta_01a2a) - Y2*sin(theta_01a2a) + b_01a$x[100], 3),
                  y = round(X2*sin(theta_01a2a) + Y2*cos(theta_01a2a) + b_01a$y[100], 3),
                  branch = rep("2a", 100),
                  thickness = seq(1/gr^2,1/gr^3, length.out = 100))

tree <- rbind(tree,b_01a2a)

theta_01a2b = theta_01a - pi/6/gr
b_01a2b <- tibble(x = round(X2*cos(theta_01a2b) - Y2*sin(theta_01a2b) + b_01a$x[100], 3),
                  y = round(X2*sin(theta_01a2b) + Y2*cos(theta_01a2b) + b_01a$y[100], 3),
                  branch = rep("2b", 100),
                  thickness = seq(1/gr^2,1/gr^3, length.out = 100))

tree <- rbind(tree,b_01a2b)

theta_01b2c = theta_01b + pi/6/gr
b_01b2c <- tibble(x = round(X2*cos(theta_01b2c) - Y2*sin(theta_01b2c) + b_01b$x[100], 3),
                  y = round(X2*sin(theta_01b2c) + Y2*cos(theta_01b2c) + b_01b$y[100], 3),
                  branch = rep("2c", 100),
                  thickness = seq(1/gr^2,1/gr^3, length.out = 100))

tree <- rbind(tree,b_01b2c)

theta_01b2d = theta_01b - pi/6/gr
b_01b2d <- tibble(x = round(X2*cos(theta_01b2d) - Y2*sin(theta_01b2d) + b_01b$x[100], 3),
                  y = round(X2*sin(theta_01b2d) + Y2*cos(theta_01b2d) + b_01b$y[100], 3),
                  branch = rep("2d", 100),
                  thickness = seq(1/gr^2,1/gr^3, length.out = 100))
?seq
tree <- rbind(tree,b_01b2d)

ggplot(tree) + 
  geom_point(aes(x, y, size = thickness)) + 
  coord_fixed() + theme(legend.position="none")
```

# Develop recursive function to make trees from deterministic inputs here.

### Input arguments

levels                 # (int) Indicates number of levels beyond starting branch. \newline
length                 # (dbl) Indicates length of a branch. \newline
scale_length           # (lgl) Indicates if lengths should be scaled at each new level. \newline
length_scale           # (dbl) Indicates rate in which branch lengths shorten at each level. \newline
splits                 # (int) Indicates number of new branches at each split. \newline
start_angle            # (dbl) Indicates angle of starting branch, measured ccw from +y direction. \newline
angle                  # (dbl) Indicates angle between each branch at a split. \neline
scale_angle            # (lgl) Indicates if branch split angles should be scaled at each new level. \newline
thickness              # (dbl) Indicates thickness of a branch. \newline
taper                  # (lgl) Indicates if branches should taper. \newline
taper_scale            # (dbl) Indicates rate of branch taper from start to end \newline

man_lengths            # Manually select branch length for starting branch and branches at each level. \newline
man_angles             # Manually select angles between branches at each split by level. \newline
man_split_thickness    # Manually select thickness of each branch at each split in order. \newline
man_begin_thick        # Manually select starting thickness. \newline
man_end_thick          # Manually select ending thickness. \newline
man_splits             # Manually select number of branches at split by level. \newline

### First try at function

```{r}

basic_deterministic_trees <- function(levels = 3, 
                                      length = 1,
                                      scale_length = T,
                                      length_scale = 1.272018,
                                      splits = 2,
                                      start_angle = 0,
                                      angle = pi/(2*splits + 2),
                                      scale_angle = F,
                                      angle_scale = 1.272018,
                                      thickness = 1,
                                      taper = T,
                                      taper_scale = 1.61803,
                                      man_lengths = 0,
                                      man_angles = 0,
                                      man_split_thickness = 0,
                                      man_begin_thick = 0,
                                      man_end_thick = 0,
                                      man_splits = 0){
  
  inputs = list(levels = levels,
                length = length,
                scale_length = scale_length,
                length_scale = length_scale,
                splits = splits,
                start_angle = start_angle,
                angle = angle,
                scale_angle = scale_angle,
                angle_scale = angle_scale,
                man_lengths = man_lengths,
                man_split_thickness = man_split_thickness,
                man_begin_thick = man_begin_thick,
                man_end_thick = man_end_thick,
                man_splits = man_splits)
  
  # Get branch length information and make table of coordinates
  X <- rep(0, 100)
  if(man_lengths){
    lengths <- man_lengths
    scale_length <- F
    Ys <- map_dfc(lengths, ~ seq(0, ., length.out=100)) %>% 
      set_names(map_chr(0:levels, ~ paste(.)))
    }
  if(scale_length){
    lengths <- map_dbl(0:(levels), ~ length/length_scale^(.))
    Ys <- map_dfc(lengths, ~ seq(0, ., length.out=100)) %>% 
      set_names(map_chr(0:levels, ~ paste(.)))
  }else{
    lengths <- rep(length, levels+1)
    Ys <- map_dfc(lengths, ~ seq(0, 1, length.out=100)) %>% 
      set_names(map_chr(0:levels, ~ paste(.)))
      }
  
  # Get branch angle information
  if(man_angles){
    angles <- man_angles
    scale_angle <- F
    }
  if(scale_angle){
    angles <- c(start_angle, map_dbl(1:levels, ~ angle/angle_scale^(. - 1)))
  }else{
    angles <- c(start_angle, rep(angle, levels))
    }
  
  # Get thickness information
  if(man_split_thickness){
    thicknesses <- c(man_begin_thick,
                     man_split_thickness,
                     man_end_thick)
    taper <- F
    ts <- map_dfc(1:(levels+1), ~ seq(thicknesses[.], thicknesses[.+1], length.out=100)) %>% 
      set_names(map_chr(0:levels, ~ paste(.)))
  }
  if(taper){
    thicknesses <- map_dbl(0:(levels+1), ~ thickness/taper_scale^(.))
    ts <- map_dfc(1:(levels+1), ~ seq(thicknesses[.], thicknesses[.+1], length.out=100)) %>% 
      set_names(map_chr(0:levels, ~ paste(.)))
  }else{
    ts <- map_dfc(1:(levels+1), ~ rep(thickness, 100)) %>% 
      set_names(map_chr(0:levels, ~ paste(.)))
    }
  
  # Get information on number of splits at each level
  if(man_splits){splits <- man_splits
  }else{splits <- rep(splits, levels)}
  
  # List to contain each branch's information
  branches <- list("0" <- )
  
}




```












