---
title: Deterministic Trees
output: github_document
---

```{r, message = F, warning = F}
devtools::load_all()
```

# Develop recursive function to make trees from deterministic inputs here.

### Input arguments

<b>splits</b>                 : (int) Indicates number of levels beyond starting branch. <br>
<b>length</b>                 : (dbl) Indicates length of a branch. <br>
<b>scale_length</b>           : (lgl) Indicates if lengths should be scaled at each new level. <br>
<b>length_scale</b>           : (dbl) Indicates rate in which branch lengths shorten at each level. Vector or single value. <br>
<b>trunk_scale</b>            : (dbl) Used to vary the relative size of the "trunk"
<b>children</b>               : (int) Indicates number of new branches at each new level. <br>
<b>start_angle</b>            : (dbl) Indicates angle in radians of starting branch, measured ccw from +y direction. <br>
<b>angle</b>                  : (dbl) Indicates angle in radian between each branch at a split. <br>
<b>scale_angle</b>            : (lgl) Indicates if branch split angles should be scaled at each new level. <br>
<b>angle_scale</b>            : (lgl) Indicates rate at which angles should decrease <br>
<b>thickness</b>              : (dbl) Indicates thickness of a branch. <br>
<b>scale_thickness</b>        : (lgl) Indicates if thickness should should shrink at each new level <br>
<b>thickness_scale</b>        : (dbl) Indicates rate in which branch thicknesses should shrink <br>
<b>taper</b>                  : (lgl) Indicates if branches should taper. <br>
<br>
<b>man_lengths</b>            : Manually select branch length for starting branch and branches at each level. <br>
<b>man_angles</b>             : Manually select angles between branches at each split by level. <br>
<b>man_split_thickness</b>    : Manually select thickness of each branch at each split in order. <br>
<b>man_begin_thick</b>        : Manually select starting thickness. <br>
<b>man_end_thick</b>          : Manually select ending thickness. <br>
<b>man_children</b>           : Manually select number of branches at split by level. <br>
<b>sib_ratio</b>              : Only works if equal number of children at each split. Indicates relative size of children. <br>
<br>
<b>title</b>                  : (chr) Optional title for output tree. <br>
<b>plot</b>                   : (lgl) Default to T for plotting <br>
<b>datadump</b>               : (lgl) Default to F. Set to T get relevant data.

### First try at function


### Testing "splits" input with others set to default
```{r}
par(mfrow=c(2,3), mar=c(1,1,1,1))
deterministic_tree(splits = 1, title = "splits = 1")
deterministic_tree(splits = 2, title = "splits = 2")
deterministic_tree(title = "default splits = 3")
deterministic_tree(splits = 4, title = "splits = 4")
deterministic_tree(splits = 5, title = "splits = 5")
deterministic_tree(splits = 6, title = "splits = 6")

# Check for improper "splits" input
rbind(deterministic_tree(splits = 0.3),
      deterministic_tree(splits = -2),
      deterministic_tree(splits = "test"))
```

### Test "children" and "man_children" with others set to default
```{r}
par(mfrow=c(2,2), mar=c(1,1,1,1))
deterministic_tree(children = 1, title = "children = 1")
deterministic_tree(title = "default children = 2")
deterministic_tree(children = 3, title = "children = 3")
deterministic_tree(children = 4, title = "children = 4")
```

```{r}
par(mfrow=c(2,2), mar=c(1,1,1,1))
deterministic_tree(man_children = c(2,3,4), title = "man_children = c(2,3,4)") # Currently experiencing issues
deterministic_tree(man_children = c(3,2,3), title = "man_children = c(3,2,3)")
# Having "man_children" length =/= "splits" changes "splits" to length.
deterministic_tree(man_children = 4, title = "man_children = 4")
deterministic_tree(man_children = c(3,3,3,3,3), title = "man_children = c(3,3,3,3,3)")
```

### The role of tapering and scaling at each split for "splits = 5"
```{r}
par(mfrow=c(2,3), mar=c(1,1,1,1))
deterministic_tree(splits = 5, title = "all = T")
deterministic_tree(splits = 5, taper = F, title = "scale_thickness = T, taper = F")
deterministic_tree(splits = 5, scale_thickness = F, taper = F, title = "scale_thickness = F, taper = F")
deterministic_tree(splits = 5, scale_length = F, title = "scale_length = F")
deterministic_tree(splits = 5, scale_angle = F, title = "scale_angle = F")

# Check for improper inputs
rbind(deterministic_tree(taper = 2),
      deterministic_tree(scale_length = "test"),
      deterministic_tree(scale_angle = 1.5))
```

### Exploring "angle_scale" with "splits = 5"
```{r}
par(mfrow=c(2,2), mar=c(1,1,1,1))
deterministic_tree(splits = 5, title = "default angle_scale = 1.127838")
deterministic_tree(splits = 5, angle_scale = 1.5, title = "scale_angle = 1.5")
deterministic_tree(splits = 5, angle_scale = 2, title = "scale_angle = 2")
deterministic_tree(splits = 5, angle_scale = 0.75, title = "scale_angle = 0.75")
```

### Exploring "length_scale" with "splits = 5" 
```{r}
par(mfrow=c(2,3), mar=c(1,1,1,1))
deterministic_tree(splits = 5, length_scale = 1.2, title = "length_scale = 1.2")
deterministic_tree(splits = 5, title = "default length_scale = 1.4")
deterministic_tree(splits = 5, length_scale = 2, title = "length_scale = 2")
deterministic_tree(splits = 5, length_scale = 0.75, title = "length_scale = 0.75")
deterministic_tree(splits = 5, length_scale = c(2,2,1.5,1,1), title = "length_scale = c(2,2,1.5,1,1)")
deterministic_tree(splits = 5, length_scale = c(1,1,1.5,2,2), title = "length_scale = c(1,1,1.5,2,2)")
```

### Exploring "thickness_scale" with "splits = 5". Starting thickness = 2 unless stated otherwise.
```{r}
par(mfrow=c(2,2), mar=c(1,1,1,1))
deterministic_tree(splits = 5, thickness_scale = 1.2, title = "thickness_scale = 1.2")
deterministic_tree(splits = 5, title = "default thickness_scale = 1.61803")
deterministic_tree(splits = 5, thickness_scale = 2, title = "thickness_scale = 10")
# Values less than 1 increase thickness
deterministic_tree(splits = 5, thickness_scale = 0.8, thickness = 0.5, title = "thickness = 0.5, thickness_scale = 0.8")
```

### Exploring "sib_lgth_ratio" -> "children" determined by length of vector "sib_lgth_ratio"
```{r}
par(mfrow=c(2,2), mar=c(1,1,1,1))
deterministic_tree(sib_lgth_ratio = c(1,2), title = "sib_lgth_ratio = c(1,2)")
deterministic_tree(sib_lgth_ratio = c(1,2,1), title = "children = 3, sib_lgth_ratio = c(1,2,1)")
# As written if branch given a length of zero, that doesn't mean it won't still have its own children
deterministic_tree(sib_lgth_ratio = c(1,0,1), title = "children = 3, sib_lgth_ratio = c(1,0,1)")
deterministic_tree(sib_lgth_ratio = c(1,2,2,1), title = "children = 4, sib_lgth_ratio = c(1,2,2,1)")
```

```{r}
par(mfrow=c(2,3), mar=c(1,1,1,1))
deterministic_tree(splits = 8, sib_lgth_ratio = c(1,2), title = "splits = 8, sib_lgth_ratio = c(1,2)")
deterministic_tree(splits = 6, sib_lgth_ratio = c(1,2,1), title = "splits = 6, sib_lgth_ratio = c(1,2,1)")
deterministic_tree(splits = 5, sib_lgth_ratio = c(1,2,2,1), title = "splits = 5, sib_lgth_ratio = c(1,2,2,1)")
deterministic_tree(splits = 5, sib_lgth_ratio = c(2,1,1,2), title = "splits = 5, sib_lgth_ratio = c(1,2,2,1)")
deterministic_tree(splits = 6, sib_lgth_ratio = c(1,2,3), title = "splits = 6, sib_lgth_ratio = c(1,2,3)")
deterministic_tree(splits = 6, sib_lgth_ratio = c(2,1,2), title = "splits = 6, sib_lgth_ratio = c(1,2,3)")
```

### Similarly, "sib_thk_ratio" effects the thickness.

```{r}
par(mfrow=c(2,3), mar=c(1,1,1,1))
deterministic_tree(splits = 8, sib_thk_ratio = c(1,2), title = "splits = 8, sib_thk_ratio = c(1,2)")
deterministic_tree(splits = 6, sib_thk_ratio = c(1,2,1), title = "splits = 6, sib_thk_ratio = c(1,2,1)")
deterministic_tree(splits = 5, sib_thk_ratio = c(1,2,2,1), title = "splits = 5, sib_thk_ratio = c(1,2,2,1)")
deterministic_tree(splits = 5, sib_thk_ratio = c(2,1,1,2), title = "splits = 5, sib_thk_ratio = c(1,2,2,1)")
deterministic_tree(splits = 6, sib_thk_ratio = c(1,2,3), title = "splits = 6, sib_thk_ratio = c(1,2,3)")
deterministic_tree(splits = 6, sib_thk_ratio = c(2,1,2), title = "splits = 6, sib_thk_ratio = c(1,2,3)")
```

### Explore "trunk_scale". It simply shrinks the starter branch. Other arguments: "splits = 6, angle_scale = 1.25, sib_lgth_ratio = c(1,5,1), sib_thk_ratio = c(1,2,1)"
```{r}
par(mfrow=c(1,3), mar=c(1,1,1,1))
deterministic_tree(splits = 6, angle_scale = 1.25, sib_thk_ratio = c(1,2,1), sib_lgth_ratio = c(1,5,1), title = "default: trunk_scale = 1")
deterministic_tree(splits = 6, trunk_scale = 0.75, angle_scale = 1.25, sib_thk_ratio = c(1,2,1), sib_lgth_ratio = c(1,5,1), title = "trunk_scale = 0.75")
deterministic_tree(splits = 6, trunk_scale = 0.25, angle_scale = 1.25, sib_thk_ratio = c(1,2,1), sib_lgth_ratio = c(1,4,1), title = "trunk_scale = 0.25")
```

```{r}

```




