---
title: Random Trees Report
author: Sean Gilligan
output: github_document
---

```{r, message = F, warning = F}
devtools::load_all()
```

## Fractals

Fractals are mathematical objects made from simple recursive processes that produce potentially infinite identical patterns across many different scales. Many fractals appear in nature, from snowflakes, nautilus shells, flowers, rivers, trees, and romanesco broccoli. The package I’ve written allows for the production of fractal trees, both deterministic and with some added randomness in a couple domains. It also allows for animated GIF production to demonstrate "growing" trees and trees "swaying" in the wind. The user can also choose to save most of the data used in tree construction and display.

```{r, fig.align='center'}
deterministic_tree(splits = 8, children = 2, angle = 9*pi/12, scale_angle = F, 
                   scale_thickness = F, taper = F, thickness = 0.5, length_scale = 1.5)
```

## Deterministic Trees

The main inputs for the function <b>deterministic_tree()</b> allow the user to decide how many splits there are, how many branches are produced at each split, the angles between branches, the thicknesses, and the lengths. In regard to the last three items there exist additional functionality to set an iterative scaling process that reduces these parameters for subsequent generations, as well produce disparities between branch siblings. Some minor demonstrations are shown below. Unless indicated otherwise all other arguments are set to their default values. For a more thorough exploration of the arguments and their effects, please see <a href="https://github.com/ST541-Fall2020/swankydoodledandy-project-randomtrees/blob/master/basic_deterministic_trees.md">basic_deterministic_trees.md</a>.

```{r, fig.align='center'}
par(mfrow=c(2,2), mar=c(1,1,1,1))
deterministic_tree(splits = 1, title = "splits = 1")
deterministic_tree(title = "default splits = 3")
deterministic_tree(splits = 5, title = "splits = 5")
deterministic_tree(splits = 7, title = "splits = 7")
```
```{r, fig.height=2, fig.align='center'}
par(mfrow=c(1,2), mar=c(1,1,1,1))
deterministic_tree(title = "default children = 2")
deterministic_tree(children = 3, title = "children = 3")
```
```{r, fig.align='center'}
par(mfrow=c(2,2), mar=c(1,1,1,1))
deterministic_tree(splits = 5, taper = F, title = "scale_thickness = T, taper = F")
deterministic_tree(splits = 5, scale_thickness = F, taper = F, title = "scale_thickness = F, taper = F")
deterministic_tree(splits = 5, scale_length = F, title = "scale_length = F")
deterministic_tree(splits = 5, scale_angle = F, title = "scale_angle = F")
```

## Random Trees

The function <b>deterministic_tree()</b> is actually a wrapper around the function <b>random_tree()</b> that turns all the default randomizing parameters off. As written, the function <b>deterministic_tree()</b> cannot introduce randomness on its own. The included randomization options in <b>random_tree()</b> allow for uniformly adding some Gaussian noise to angles and lengths for branches. Variances can be set by the user, but reasonable default values are included as well. A brief exploration is shown below. For more information please see <a href="https://github.com/ST541-Fall2020/swankydoodledandy-project-randomtrees/blob/master/random_trees.md">random_trees.md</a>. Also on the other side of this link is a timing comparison between the current function code and an older iteration. The system time difference achieved by vectorization of tree construction is on the order of 10.

```{r, fig.align='center'}
titles <- rep(c("both = F", "random_angles = T", "random_lengths = T", "both = T"), each = 4)
ras <- rep(c(F,F,F,F,T,T,T,T), 2)
rls <- c(rep(F,8),rep(T,8))
```

#### splits = 8, children = 2, angle = pi/4, scale_angle = F, length_scale = 1.4
```{r, fig.height = 5, fig.align='center'}
par(mfrow=c(4,4), mar=c(1,1,1,1))
for(i in 1:16){
  random_tree(splits = 8, children = 2, angle = pi/4, scale_angle = F, length_scale = 1.4, random_angles = ras[i], random_lengths = rls[i], title = titles[i])
}
```

## Saving tree data

The data of a generated tree can be returned for user use by setting the argument <b>datadump = T</b>. This feature is required for the use of the provided animation functions. An additional function <b>plot_tree()</b> can be used to plot the stored output in the form in which it is given to the user. Here is an example in which the argument <b>plot = F</b> means the figures of these trees will not be shown upon construction.

```{r}
fractal_tree1 <- random_tree(splits = 9, children = 2, angle = pi/4, sib_lgth_ratio = c(1.5,1), sib_thk_ratio = c(1,1.5), 
                             angle_scale = 1.05, length_scale = 1.35, plot = F, datadump = T, title = "fractal_tree1")
fractal_tree2 <- deterministic_tree(splits = 7, trunk_scale = 0.25, angle_scale = 1.25, sib_thk_ratio = c(1,2,1), 
                                    sib_lgth_ratio = c(1,5,1), plot = F, datadump = T, title = "fractal_tree2")
fractal_tree3 <- random_tree(splits = 7, sib_lgth_ratio = c(1,2,1), angle = pi/6, plot = F, datadump = T, title = "fractal_tree3")
```

The function <b>plot_tree()</b> is now called to plot it.

```{r, fig.align='center', fig.width=15}
par(mfrow=c(1,3), mar=c(1,1,1,1))
plot_tree(fractal_tree1)
plot_tree(fractal_tree2)
plot_tree(fractal_tree3)
```


## Animating trees

This package includes two functions for animating trees. 

The first is <b>swaying_tree()</b>. This function takes as input one saved tree output, randomization information for the "wind", and a logical input telling the function to output the name of the created file in the form of string. As stated before, the file type is a GIF. A folder titled "swaying_trees" is generated in the current working directory where generated files will be placed. Similarly, for the function <b>growing_tree()</b>, a folder "growing_trees" is generated. This function simply plots the tree data in an order that makes it appear to be growing. It takes the same inputs as <b>swaying_tree()</b>, minus the randomization information. To see an example of these functions in action, including embedded GIFs, please see <a href="https://github.com/ST541-Fall2020/swankydoodledandy-project-randomtrees/blob/master/animated_tree.md">animated_tree.md</a>. 

An example of <b>swaying_tree()</b>'s "wind" is shown below. The output values are mapped to angle modifications to each branch as they "move" along the random field, or as the field "moves" along them.

```{r, fig.align='center'}
model <- RandomFields::RMexp(var = 0.02, scale = 0.4)
branch_count <- sum(cumprod(fractal_tree1$fun_variables$children)) + 1
x <- seq(0, 10, length.out = 50)
y <- seq(0, 10, length.out = branch_count)
simu <- suppressMessages(as.matrix(RandomFields::RFsimulate(model, x, y, grid=TRUE)))

raster::plot(raster::raster(simu))
```